Consistent Polyhedral Surrogates via Embedding

### 2019-05-19 notes/jessie-proof-sketches.tex
comments on jessie proof sketches

Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$ onto $\simplex$ for a discrete loss $\ell$.
For a facet $f$, we also consider $u_f = \argmin_r \ell(r, p)$ for any $p \in \inter{f}$.
(We know that this $u_f$ is the same regardless of the choice of $p$ since $\risk{\ell}$ has a constant, well-defined derivative on $\inter{f}$) 
\hrule
\hrulefill
\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  \jessie{Ready for a look over.}
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}[Property version]
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.

@@

@@

  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$.
  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.

>>>>

Throughout this section, consider $F$ to be the facets of the projection of the surface of $\risk{\ell}$ onto $\simplex$ for a discrete loss $\ell$.
For a facet $f$, we also consider $u_f = \argmin_r \ell(r, p)$ \raf{be careful: $\in \argmin$} for any $p \in \inter{f}$.
(We know that this $u_f$ is the same \raf{not sure about ``same'', maybe ``an element of the argmin''} regardless of the choice of $p$ since $\risk{\ell}$ has a constant, well-defined derivative on $\inter{f}$)
\raf{Cite why we know this; it's in the COLT appendix}
\hrule
\hrulefill
\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  \jessie{Ready for a look over.}
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}[Property version]
  \raf{Forward: you had the right idea that this is mainly Lemma 11.  But you have to step through the logic much more carefully, and be rigorous.  Keep in mind: you already have $\varphi$ from the embedding, and you know the loss values match.  It's true that you need to map $u$ values to $r$ values, but what you have doesn't make sense.}

  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.

@@

  \raf{Reverse: The high-level idea is that the projections (power diagrams) of $\risk{\ell}$ and $\risk{L}$ are the same, so since $\prop{\ell}$ has finitely many full-dimensional level sets, so does $\prop{L}$.  The property part of the embedding then follows; just take any $u_f$ like you have.  It remains to show that the losses themselves must match up; this is what the FK result is useful for.  Note though that you can't conclude that the minimizers are unique (and it's not true) since $\prop{L}$ is not redundant, as assumed in that paper.
    All that said, I'm pretty confused by what you are trying to do; seems like your contradiction is going the wrong way, and several steps are missing justification.}

@@

  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
